Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-03-16 pldi14/macros_part2.tex
Change theorem setup to allow restating theorems
Misc new notation/revisions
Also few notations needed later.
Smaller box at theorem end
It's the default for thmtools and it fits better with the typesetting
done by this package (it seems the bigger box overlaps more often, but
this is not confirmed).
Enable cref on multiple "theorems"
I needed plugin requirements but set all of them up.

% Theorems, lemmas, corollaries
% Typeset in roman to avoid known TeX feature
% (bad spacing between italic text and math formulas)
%
% Numbering:
% Theorem 3.1. It always rains.
% Lemma 3.2. If it rains, then the weather is bad.
% Corollary 3.3. The weather is always bad.
%
% http://tex.stackexchange.com/a/67251
\theoremstyle{definition}
\input{pldi14/QED}
\newtheorem{theorem}{Theorem}
% http://tex.stackexchange.com/a/45358/1340
% \numberwithin{section}{chapter} % From AMS Author FAQ (http://www.ams.org/faq?class_id=561), makes no difference?
\numberwithin{theorem}{section}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

\begin{oldSec}
\newtheorem{parameter}[theorem]{Plugin Requirement}
\end{oldSec}

>>>>

% Theorems, lemmas, corollaries
% Typeset in roman to avoid known TeX feature
% (bad spacing between italic text and math formulas)
%
% Numbering:
% Theorem 3.1. It always rains.
% Lemma 3.2. If it rains, then the weather is bad.
% Corollary 3.3. The weather is always bad.
%
% http://tex.stackexchange.com/a/67251
\theoremstyle{definition}
% \input{pldi14/QED}
\theoremsymbol{\ensuremath{_\Box}}
\declaretheorem[numberwithin=section,refname={Theorem,Theorems}]{theorem}
\declaretheorem[numberlike=theorem,refname={Lemma,Lemmas}]{lemma}
\declaretheorem[numberlike=theorem,refname={Corollary,Corollaries}]{corollary}
\declaretheorem[numberlike=theorem,refname={Definition,Definitions}]{definition}
% \declaretheorem[numberlike=theorem,name=Plugin Requirement]{parameter}
\declaretheorem[numberlike=theorem,name=Plugin Requirement,refname={Plugin Requirement,Plugin Requirements}]{requirement}
% \newtheorem{theorem}{Theorem}
% % http://tex.stackexchange.com/a/45358/1340
% % \numberwithin{section}{chapter} % From AMS Author FAQ (http://www.ams.org/faq?class_id=561), makes no difference?
%\numberwithin{theorem}{section}
% \newtheorem{lemma}[theorem]{Lemma}
% \newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{definition}[theorem]{Definition}
% \newtheorem{parameter}[theorem]{Plugin Requirement}
